IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks

### 2016-07-06 ms_infocus.tex
Minor edits.

Th trait matching between HPL and EFL is crucial in this type of interaction and determines its outcome in terms of fitness for both partners. Nilsson \citep{Nilsson:1988} demonstrated experimentally that shortening the nectary tube of long-spurred corollas decreased both seed set and pollinia removal for \textit{Platanthera} orchids. Further experimental evidence has been provided for long-tongued nemestrinid flies pollinating long-tubed irises in South Africa, where increased mismatch decreases both plant fitness and the nectar extraction efficiency of the pollinators \citep{Pauw:2009}. Sazatornil \textit{et al.} extend those results to the scale of the whole moth-plant assemblage and demonstrate that trait matching successfully predicts the diversity of interactions recorded. Interestingly enough, the interaction patterns in two local assemblages from ecotone areas of the Chaco woodland-Yungas montane rain forest transition are better fitted by a neutral model where pairwise interactions are driven by probability of interspecific encounter.

@@

Yet Sazatornil \textit{et al.} did not include the morphological difference for parameter estimation when interactions were not recorded. Thus the test of the mismatch hypothesis implicitly includes forbidden links effects: a full mismatch of corolla tube/proboscis lengths actually means a forbidden link. In any case the mismatch hypothesis somehow captures the fact that a fraction of the unobserved interactions in these hawkmoth/flower assemblages is due to extreme phenotypic mismatch (i.e., size-related forbidden links).

>>>>

Th trait matching between HPL and EFL is crucial in this type of interaction and determines its outcome in terms of fitness for both partners. Nilsson \citep{Nilsson:1988} demonstrated experimentally that shortening the nectary tube of long-spurred corollas decreased both seed set and pollinia removal for \textit{Platanthera} orchids. Further experimental evidence has been provided for long-tongued nemestrinid flies pollinating long-tubed irises in South Africa, where increased mismatch decreases both plant fitness and the nectar extraction efficiency of the pollinators \citep{Pauw:2009}. Sazatornil \textit{et al.} extend those results to the scale of the whole moth-plant assemblage and demonstrate that trait matching successfully predicts the diversity of interactions recorded. Interestingly enough, the interaction patterns in two local assemblages from ecotone areas of the Chaco woodland-Yungas montane rain forest transition are better fitted by a neutral model where pairwise interactions are driven by probability of interspecific encounter. Yet Sazatornil \textit{et al.} did not include the morphological difference for parameter estimation when interactions were not recorded. Thus the test of the mismatch hypothesis implicitly includes forbidden links effects: a full mismatch of corolla tube/proboscis lengths actually means a forbidden link. Furthermore,  a fraction of unobserved interactions was likely caused by phenological uncoupling between flowering and hawkmoth activity phenophases \citep{BasJor:2014,Sazatornil:2016}. In any case the mismatch hypothesis somehow captures the fact that a fraction of the unobserved interactions in these hawkmoth/flower assemblages is due to extreme phenotypic mismatch (i.e., size-related forbidden links) \citep{Sazatornil:2016}.

@@
